---
title: "Untitled"
author: "Poromendro Nath Burman"
date: "1/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**1. Import the library**
```{r}
library(Seurat)
```

**2. Import Data**
```{r}
# load the UMI matrix
pbmc.umis <- readRDS("./pbmc_umi_mtx.rds")

# load the HTO count matrix
pbmc.htos <- readRDS("./pbmc_hto_mtx.rds")
```

**3. Set up seurat object for the HTO data**
```{r}
# setup seurat object
pbmc.hashtag <- CreateSeuratObject(counts = pbmc.umis)

# normalize RNA data with log normalization
pbmc.hashtag <- NormalizeData(pbmc.hashtag)

# find variable features
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")

# scale variable features
pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))
```

**4. Add HTO data as an independent assay**
```{r}
# add HTO data as a new assay
pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = pbmc.htos)

# normalize the HTO data
pbmc.hashtag <- NormalizeData(pbmc.hashtag, assay = "HTO", normalization.method = "CLR")
```

**5. Demultiplex**
```{r}
pbmc.hashtag <- HTODemux(pbmc.hashtag, assay = "HTO", positive.quantile = 0.99)
```

**6 Visualize the demultiplex results**

**a. global classification results**
```{r}
table(pbmc.hashtag$HTO_classification.global)
```

**b. group cells based on max HTO signal**
```{r}
Idents(pbmc.hashtag) <- "HTO_maxID"
RidgePlot(pbmc.hashtag, assay = "HTO", features = rownames(pbmc.hashtag[["HTO"]])[1:2], ncol = 2)
```

**c. Visualize pairs of HTO signals for mutual exclusivity in singlets**
```{r}
FeatureScatter(pbmc.hashtag, feature1 = "hto_HTO-A", feature2 = "hto_HTO-B")
```

**d. compare UMIs for singlets, doublets and negative cells**
```{r}
Idents(pbmc.hashtag) <- "HTO_classification.global"
VlnPlot(pbmc.hashtag, features = "nCount_RNA", pt.size = 0.1, log = TRUE)
```

**e. tSNE**
```{r}
# remove negative cells
pbmc.hashtag.subset <- subset(pbmc.hashtag, idents = "Negative", invert = TRUE)

# calculate and plot tSNE
DefaultAssay(pbmc.hashtag.subset) <- "HTO"

pbmc.hashtag.subset <- ScaleData(pbmc.hashtag.subset, features = rownames(pbmc.hashtag.subset), verbose = FALSE)

pbmc.hashtag.subset <- RunPCA(pbmc.hashtag.subset, features = rownames(pbmc.hashtag.subset), approx = FALSE)

pbmc.hashtag.subset <- RunTSNE(pbmc.hashtag.subset, dims = 1:8, perplexity = 100)

DimPlot(pbmc.hashtag.subset, split.by = "HTO_classification.global")
```

**f. Heatmap**
```{r}
HTOHeatmap(pbmc.hashtag, assay = "HTO", ncells = 5000)
```




